### 2023-03-24 submission/manuscript.Rmd
Generate skewed distributions for all effect sizes

The analysis of Simulation A in WNWN used clustering accuracy to assess the effect of different normalization procedures, distance calculations, and clustering methods. There has been controversy over the meaning of clustering samples (i.e., enterotypes) including whether such clustering should be done on ecological distances or sequence counts and the biological interpretation of such clusters [XXXXXXXXX]. One notable challenge with using clustering accuracy as the dependent variable is that the clustering methods force the samples into one of two clusters. For the case where the effect size was 1.0, it was impossible for all 80 samples to be assigned to a single cluster. As has already been demonstrated, an additional challenge with using clustering accuracy is that there is sensitivity to the clustering method that a researcher selects. Given the apparent interaction between the various variables and clustering method with clustering accuracy, an alternative approach is needed. In fact, a more common analysis of distance matrices would be to use a non-parametric analysis of variance test of the various distance matrices. Therefore, I subjected each of the distance matrices to such a test using `adonis2`, a function from the vegan R package that implements this test. This analysis allowed me to quantify the probability of falsely rejecting a null hypothesis (i.e., Type I error) when the effect size was 1.0 and the power to detect a difference when the effect sizes were larger than 1.0. Such an analysis was not possible in the original study since only 5 replicates of each simulation were performed.

>>>>

The analysis of the GlobalPatterns-based simulations in WNWN used clustering accuracy to assess the effect of different normalization procedures, distance calculations, and clustering methods. There has been controversy over the meaning of clustering samples (i.e., enterotypes) including whether such clustering should be done on ecological distances or sequence counts and the biological interpretation of such clusters [XXXXXXXXX]. One notable challenge with using clustering accuracy as the dependent variable is that the clustering methods force the samples into one of two clusters. For the case where the effect size was 1.0, it was impossible for all 80 samples to be assigned to a single cluster. As has already been demonstrated, an additional challenge with using clustering accuracy is that there is sensitivity to the clustering method that a researcher selects. Given the apparent interaction between the various variables and clustering method with clustering accuracy, an alternative approach is needed. In fact, a more common analysis of distance matrices would be to use a non-parametric analysis of variance test of the various distance matrices. Therefore, I subjected each of the distance matrices to such a test using `adonis2`, a function from the vegan R package that implements this test. This analysis allowed me to quantify the probability of falsely rejecting a null hypothesis (i.e., Type I error) when the effect size was 1.0 and the power to detect a difference when the effect sizes were larger than 1.0. Such an analysis was not possible in the original study since only 5 replicates of each simulation were performed.
